---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# queimadas

<!-- badges: start -->
<!-- badges: end -->

The goal of `queimadas` is to provide tools for analyzing and reporting data
from wildfires in Brazil. These data aids during the selection of the
reference data used by the *Programa Queimadas* at the National Institute for
Space Research in Brazil.

## Installation

You can install the development version of queimadas from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("albhasan/queimadas")
```

## Examples

This example shows how to create a database with sample data from queimadas.

```{r example}
library(queimadas)

# List CSV files with data.
csv_files <-
  list.files(
    path = system.file("extdata", "sample_csv", package = "queimadas"),
    pattern = "*csv",
    recursive = TRUE,
    full.names = TRUE
  )

# Create a file database. 
db_con <- DBI::dbConnect(
  drv = RSQLite::SQLite(),
  dbname = tempfile(pattern = "queimadas.sqlite_")
)

# Load sample data to the database.
load_database(
  db_con = db_con,
  file_paths = csv_files,
  c_types = "ddccccccdnncd",
  table_name = "fire_foci",
  disconnect = TRUE
)
```
